DisCon Kids Pilot

### 2019-03-01 analysis/02_kids_600.Rmd
add kids data

#data <- read_csv(file="../data/kids_600.data.csv")
```

@@

ggplot() +
  geom_jitter(data = p3, aes(x = subage, y = correct, col = subage, alpha = .2),width = .2,height = .01)+
  geom_pointrange(data = p4, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct in training")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized()
```

@@

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_jitter(width = .01,height = .01, alpha = .5)+
  geom_smooth(method = "lm",  se = T,  alpha = .5, size = .6, span = 2)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct choice")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)
```

@@

```{r}
plot_post <- data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1))%>%
  summarise(correct = list(correct)) %>%
  group_by(subage) %>%
  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 10000)[,"mu"])))%>%
  select(-correct)

@@

plot_dens <- data_frame(
  age = rep(c(3,4), each = 10000),
  posterior = c(unlist(plot_post%>%filter(subage == "3") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "4") %>% pull(posterior)))
)

>>>>

data <- read_csv(file="../data/kids_600.data.csv")
```

@@

ggplot() +
  geom_jitter(data = p3, aes(x = subage, y = correct, col = subage, alpha = .2),width = .2,height = .01)+
  geom_pointrange(data = p4, aes(x = subage, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  guides(alpha = F)+
  scale_color_solarized(name = "Age")
```

@@

ggplot(data = p5, aes(x = age_num, y = correct)) +
  geom_jitter(width = .01, height = .0, alpha = .5)+
  geom_smooth(method = "lm",  se = T,  alpha = .5, size = 1, col = "darkred", fill = "darkgreen", alpha = .5 )+
  geom_hline(yintercept = 1/3, lty=2)+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(3,5)+
  guides(alpha = F)
```

@@

```{r}
plot_post <- data %>%
  filter(phase != "training") %>%
  group_by(subage,subid) %>%
  summarise(correct = mean(correct_target1))%>%
  summarise(correct = list(correct)) %>%
  group_by(subage) %>%
  mutate(posterior = list((ttestBF(unlist(correct), mu = 1/3, posterior = T, iterations = 1000)[,"mu"])))%>%
  select(-correct)

@@

plot_dens <- data_frame(
  age = rep(c(3,4), each = 1000),
  posterior = c(unlist(plot_post%>%filter(subage == "3") %>% pull(posterior)),unlist(plot_post%>%filter(subage == "4") %>% pull(posterior)))
)
